---
title: "PCM_out_cov_aux_descriptives"
output: pdf_document
---

```{r}
install.packages("pastecs")
library(pastecs)

```




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file contains descriptives of the variables that are included in the PCM_outcomes_covs_aux files, that are not included in the summary statistics


interanlising age at ~10y (in months)
```{r}
summary(as.numeric(as.character(alspac.table$kv9991a)))

```

internalising score at 10y 
```{r}
summary(as.numeric(as.character(alspac.table$kv8603)))
```

fatmass age ay ~10y (in months)

```{r}
summary(as.numeric(as.character(alspac.table$f9003c)))
```

trunk fatmass (in grams) from DXA scan at ~10y 
```{r}
summary(as.numeric(as.character(alspac.table$f9dx126)))
```

 Smoked cigarettes reguarly during last 2 months of pregnancy (n = 11710)
```{r}
summary(alspac.table$e170)
```

Maternal alcohol consumption during prenancy, between 1-3 months and 7-9 months
```{r}
summary(alspac.table$b721)
summary(alspac.table$e220)

```
Ethnicity of the mother and father 
```{r}
summary(alspac.table$c800)
summary(alspac.table$c801)

```
Variables to construct pre-pregnancy BMI score incl. pre-pregnancy weight (kg), and respondant height (cm)
```{r}
summary(as.numeric(as.character(alspac.table$dw002)))
summary(as.numeric(as.character(alspac.table$m4221)))

summary(alspac.table$bmi_0)
```

in comparison with the maternal BMI variable**1.5
```{r}
summary(as.numeric(as.character(alspac.table$dw043)))

```
bmi_1, which uses birthweight of mother, birthweight of child, and height of mother to calculate BMI of mother during pregancy. 

```{r}
summary(alspac.table$bmi_1)
```

age of mother at birth 
```{r}
summary(as.numeric(alspac.table$bestgest))
```

gestational weight at birth 

```{r}
summary(as.numeric(as.character(alspac.table$kz030)))
```

maternal age at input 
```{r}
summary(as.numeric(alspac.table$mz028b))
```

maternal depression cont. 18w gest - 21m

```{r}
summary(alspac.table$b370)
summary(alspac.table$c600)
summary(as.numeric(alspac.table$e390))
summary(as.numeric(alspac.table$f200))
summary(as.numeric(alspac.table$g290))
```

paternal depression cont. 18w gest - 21m

```{r}
summary(alspac.table$pb260)
summary(alspac.table$pc102) 
summary(as.numeric(alspac.table$pd200))
summary(as.numeric(alspac.table$pe290))
```